Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment

### 2017-12-16 paperDraft3.tex
draft sent to Wilson

In this paper, we propose an alternative approach using a Bayesian hierarchical
model.  We will begin by introducing a hierarchical structure that models the
relationships in the data across all test phases and incorporates known
similarities between vehicle failure modes.  Next, we will consider different
distributional assumptions and their implications.  We will also
discuss model diagnostics to consider when choosing a final model. Then we will
use the JLTV data to illustrate this process and discuss system reliability
results. This will lead us into the next section on using these results to
improve the planning of future test.

In this reliability setting we are analysing time to failure data measured in
miles for a multiple component system with the primary interest in the system
failure rate and future failure counts.  The most common models used in this
failure rate analysis are lifetime distributions and the most common for failure
count analysis is the \emph{Poisson process} counting model.  We will utilize
both and the relationships between them.

The methodology section is organized as follows.  Section 3.1 describes the
reliability modeling process, breaking it down into five subsections.  First, we
introduce the general structure we will be using along and how to account for
the correction period between phases.  Then we move onto distributional
assumptions and model diagnostics which we illistrate with the JLTV case study
data.  In section 3.2 we discuss methods of designing next stage test plans.
First we outline the traditional approaches, then we walk through a Bayesian
approach that allows the practitioner to incorperating the models developed from
section 3.1 with the hopes of reducing testing resources required while still
minimizing producer and consumer risks.

\subsubsection{Model Structure}
Introducing notation, for each phase of testing we have failure mileage data for
a given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the end of that
testing phase. In each phase of testing, we assume the vehicle miles between
failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a lifetime distribution with
an unknown set of parameters that include a rate parameter.  For the first phase
the rate parameter for vehicle $i$ and failure mode $j$ will be denoted as
$\lambda_{ij}$.  Then for the next stage we will use the same $\lambda_{ij}$ but
add a multiplicative correction parameter $\rho_{1,j}$ that represents the
change in this rate due to the CAP.  This proceedure is then repeated for each
subsequent stage.  The correction parameter will be discussed more in the next
section but the general model is as follows,
\begin{align*}
\text{Phase 1: }&y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
j=1,2,...,s \quad k=1,2,...,n_{ij}\\
\text{Phase 2: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\sim f(\cdot) \\
\text{Phase 3: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\rho_{j}^{P3}\sim f(\cdot)
\end{align*}
where $v$ represents the number of vehicles, $s$ is the number of failure modes,
and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$. The
number of failure modes is assumed fixed and known \textit{a priori}.

For this model we will assume a prior distribution on failure rate parameter
$\lambda_{ij}$.  This distribution depends on whether failure mode $j$ is
considered to be common across vehicles or related but not identical. For the
related failure modes, we place a prior distribution on the collection of
$\lambda_{ij}$; in other words, we assume each vehicle has a distinct failure
rate in failure mode $j$ but they arise from a common distribution.  If failure
mode $j$ is considered common across vehicles, the collection of failure rates
is collapsed to a single parameter, $\lambda_{ij} = \lambda_j$. As with the
related failure modes, a prior distribution is placed on the single failure
rate. The prior distributions are independent across failure mode, and can
potentially have different hyperparameters.

% not sure we need this paragraph %
The Phase 1 analysis yields an estimate of the failure rate $\lambda_{ij}$ for
each of the vehicles for failure modes that are related.  We are assuming the
vehicles are conditionally independent, if we also assume the miles at failure
come from an exponential distribution the overall failure rate across all
failure modes can be easily calculated by $\sum_{j}\lambda_{j}$ to give us the
system failure rate.  The exponential distribution is commonly used in
reliability analysis because of its convenience, but as we will discuss in later
sections it can be unrealistic in many real-world situations.

@@

One normal assumption used in reliability growth modeling is nondecreasing
failure rates; that is either the fixes were effective or had no effect, but did
not degrade the family of vehicles.  This should generally be the case, but
because we are dealing with complex systems and testing conditions are rarely
completely consistent, we will sometimes see decreases in failure rates after
adjustments are made.  Thus we will choose a prior distribution for the
correction parameter $\rho_{j}^{P2}$ that has positive support.  If
$\rho_{j}^{P2}$ is less than one, this represents an improvement in reliability.
And the same thinking is applied to $\rho_{j}^{P3}$ for the correction period
between phases two and three.  With this structure we can use the posterior
distributions of the correction parameters to make infrence on the effectiveness
of the repairs and the join posterior distributions to evaluate the overall
system reliability within each phase.

@@

This is by far the most common parametric distribution used in reliability
modeling because of its desirable math mathematical properties and simple
interpretations.  One of these properties is that the hazard rate is constant.
For the JLTV, setting this would assume that a given component is equally likely
to fail in the first mile of testing as it is in the thousandth.  This may be
reasonable for some reliability settings, but in most setting we observe either
a decreasing hazard rate where failures are likely to occur early in testing
but less likely as the test goes on, or increasing hazard rate where we see the
system wear down as the test goes on.

Despite its common uses the assumption of a constant hazard rate over time is
rarely justifiable.  It has been well documented the issues that can arise when
this assumption is violated ~\cite{ref3}.  Thus we will also consider the same
hierarchical model structure while using the Weibull distribution.  Now we
assume that the failure mileage $t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$
distribution with scale parameter $\lambda$ and shape parameter $\gamma$, with
probability density function,
\begin{equation*}
    f(t_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
    t_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} t_{ijk}^{\gamma_{i}}).
\end{equation*}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\gamma_{j}$.  The exponential is a special
case of the Weibull, when $\gamma = 1$.  You should notice here we are now
modeling the actual failure mileage $t_{ijk}$ instead of the miles between
failures $y_{ijk}$.  This means we are treating all intra-test repairs as "bad
as old".  We could have continued with the miles between failures and assumed
"good as new" repairs, but "bad as old" modeling will be more convenient for
developing assurance test plans in later sections.  This distinction is
important in the Weibull case because the failure rate is not constant in time.
In practice the decision on intra-test repair assumptions should be made based
on the application.  In many cases repairs should be treated as somewhere
between "good as new" and "bad as old".  This requires more complex modeling
that is beyond the scope of this paper.

@@

\subsubsection{JLTV Reliability}
So far we have discussed a number of different models and the assumptions that
accompany them.  Using McMC we can fit each of these models to the JLTV dataset.
Then we can use the posterior distributions of the systems parameters to
estimate reliability-related quantities of interest for each of the eight
vehicle types.  We are able to look at a number of different statistics related
to reliability at both the component and system level.  In this study our main
quantity of interest is expected miles to  failure.  In figure 1 we have box
plots and summary statistics from the posterior distributions of the expected
miles to failure for one of the vehicle types for each of the three phases,
first using the exponential model and second using the more general Weibull
model.

@@

You can see the posterior distributions from the Weibull model have a good
amount more spread than the exponential.  This is somewhat expected given the
Weibull model is estimating two model parameters to the exponentials one, but
what is concerning is that the center of the distributions is also quite
different between the two models.  All of the Weibull EMTF posterior means are
higher than the exponentials.  This is the first sign that the exponential model
may not be a good fit to the data.

\subsubsection{Model Diagnostics}
As seen in the last section with the JLTV data, the decision of which model to
use can have a drastic impact on reliability assessment and future test
planning.  We will now look at a few  goodness-of-fit methods that can be used
to help in this decision.  The first model selection question we will explore is
the parametric form, exponential versus Weibull.  In statistical modeling we
often face the trade-off between fit and interpretability, and this situation is
no different. Because the Weibull is a more flexible model, it will always, in a
sense, fit the data better, but this comes at a price.  The exponential's
convenient form makes both computation and interpretation straightforward.  When
the Weibull's shape parameter is introduced this advantage is lost.  Thus, when
the overall fit is close to the same between the exponential and the Weibull we
will default to using the exponential.

The first check we used to decide between the exponential and Weibull models is
to fit the Weibull model and look at the posterior distributions of the shape
parameters and determine if one is a reasonable value.  Looking at the plot in
figure 2 below from the Weibull model fit with the JLTV data, we see that one is
not a reasonable value for any of the 20 failure modes.  This is our first clue
that the exponential model will not be a good fit to this data.

\begin{figure}[h]
  \centering
      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
  \caption{Posterior Plots of Shape Parameter}
\end{figure}

This is not a surprising result, because the exponential model assumes constant
failure rate.  For most vehicle failure modes we would expect the failure rate to
increase as the distance driven grows larger, and this corresponds with a shape
parameter between zero and one.  On the other hand, when the shape parameter is
larger than 1, the failure rate will decrease with time/distance.

Now a more formal diagnostic tool, the Deviance information criterion (DIC).
This is a popular method for comparing the goodness of fit of multiple models.
The DIC method gives a slight penalty for larger numbers of parameters.  The DIC
value is a unit-less measure with lower values indicating a better fit to the
data.  In the table below we show the DIC results for the different distribution
and structure combinations, we considered with the JLTV dataset.

% need to recheck these numbers %
\begin{table}[h]
\centering
\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Common Rate Model                     & 21,264.19             \\
              & Hierarchical Rate Model               & 21,244.47             \\
Weibull       & Common Rate Model                     & 20,658.25             \\
              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
\hline
\end{tabular}
\end{table}

Here we have shown that the hierarchical Weibull model fits the data much better
than the exponential, but in general information criteria comparisons do not
tell us if the model is truly a good representation of the underlying process.
The last method we present is called posterior predictive checking ~\cite{ref4}.
Here we are given important features of the data that we would expect to see if
the experiment was repeted.  In the JLTV case one feature we were interested in
was the number of miles between failure observations that were less than 140
miles.  We then used the final models to simulate 5,000 new datasets for
vehicles tested over the same number of miles for each of the three phases. We
then plot the resulting distributions for each of the 8 vehicles for all 3
phases.  In Figure 3 are two examples of the boxplots produced, one from the
exponential model (left) and one from the Weibull model (right), with the dashed
line showing where the value from the observed dataset fell.  For this method we
don’t expect all of the true values to fall in the center of the distribution.
Some values in the tales are to be expected in a random processes like this one,
but when we see many observations in the tails, as we do with the exponential,
we should consider other modeling options.

@@

\subsection{Assurance Test Planning}
In this section, we will use the reliability models fit in section two section
to develop a plan for future testing.  Here the objective is to demonstrate that
at a desired level of confidence, the system will meet or exceed a specified
requirement. The methods to be employed will be similar to the assurance testing
as discussed by Hamada et al. ~\cite{ref5}. Bayesian \emph{reliability assurance
tests} are used to ensure that the reliability of an item meets or exceeds a
specified requirement with a desired probability. Meeker and Escobar
~\cite{ref6} established the difference between this and the more traditional
\emph{reliability demonstration test}.  The difference being that the assurance
test plan incorporates supplementary data and information, where the
demonstration test only uses test data.

In both test planning methods we are interested in controlling error rates while
minimizing the resources required for testing.  In the DoD acquisition process,
the error rates will be referenced in terms of risk. \emph{Consumer risk} which
considers the event of purchasing a product that does not meet reliability
requirements.  \emph{Producer risk} which considers the event of a product with
acceptable reliability failing a given test and not being considered for
purchase.  Introducing the notation for this section, in the JLTV case study, we
will be determining how many miles on test $T$, are required and how many system
failures to allow $c$, before the product is considered unacceptable.  We will
define $W(t)$ as a random variable that represents the total number of system
failures after $t$ miles.  We will let $\pi$ denote some quantity of interest
that is related to system reliability at a given time. It is common to base both
classical and Bayesian test plans on two specified levels of $\pi$: $\pi_0$, an
\emph{acceptable reliability level} (ARL), and $\pi_1$, a \emph{rejectable
reliability level} (RRL), where $\pi_1 \leq  \pi_0$. Although the precise
definition of ARL and RRL differ between the classical and Bayesian test
criteria, we use them in an equivalent way.

\subsubsection{Classical Approach}
In the frequentest (classical) version we will use two criteria in determining
the test plans. The \emph{producer's risk}, defined as the probability of
failing the test under the null hypothesis $\pi = \pi_0$, and the
\emph{consumer's risk}, defined as the probability of passing the test under an
alternative hypothesis $\pi = \pi_1$.  Suppose that we specify a maximum value,
$\alpha$, of the producer's risk and a maximum value, $\beta$, of the consumer's
risk. For test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failures $W(t)$ and the reliability $\pi$.  Then we can simply find
the combinations of these probabilities by simultaneously solving these two
equations.  In the case where the component failure times are assumed to be
exponentially distributed with rate parameter $\lambda_i$ the failure counts for
each component come from a homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
this purely classical approach.

\subsubsection{Bayesian Approach}
Traditional methods for determining the testing procedure only rely on
distributional assumptions and/or asymptotic results. With a Bayesian approach we
incorporate the supplementary data from the previous testing phases with the
hopes of minimizing the resources needed for testing.

@@

For a test that fails, the \emph{posterior producer's risk} is the probability
that $\pi \geq \pi_{0}$, or $P \text{(}\pi \ge \pi_0 \vert \text{Test Is
Failed)}$. Notice that this is simply the posterior probability that $\pi \ge
\pi_0$ given that we have observed more than $c$ failures. In the exponential
case, if we let $\pi$ be the system failure rate $\lambda_S$, then using Bayes'
Theorem, and assuming a maximum allowable posterior producer's risk $\alpha$, an
expression for the posterior producer's risk for the exponential test plan
$(T,c)$ is
$$
\begin{aligned}
    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S
    \geq \lambda_0 \; \vert \; W > c) \\ &= \int_{\lambda_0}^{\infty}
    p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{\lambda_0}^{\infty}
    \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty} f(W > c \vert \lambda_S)
    d\lambda_S} d\lambda_S \\ &= \frac{\int_{\lambda_0}^{\infty} 1 - [ \sum_{W=0}^c
    \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
    {\int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
\end{aligned}
$$
\\
\\
For simplicity we if fix c to be zero and then perform Monte Carlo integration
using N posterior draws $ \lambda_S^{(j)} $
$$
\begin{aligned}
	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &=
	 \frac{\int_{\lambda_0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S}
	 {\int_{0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\ &\approx
	 \frac{\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq
	 \lambda_0)} {\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)} \end{aligned}
$$

Similarly, given that the test is passed, the \emph{posterior consumer's risk}
is the probability that $\pi \leq \pi_1$, or $P \text{(}\pi \leq \pi_0 \vert
\text{Test Is Passed)}$. Notice that this is simply the posterior probability
that $\pi \leq \pi_1$ given that we have observed no more than $c$ failures. In
the exponential case, if we let $\pi$ be the system failure rate $\lambda_S$,
then using Bayes' Theorem, and assuming a maximum allowable posterior consumer's
risk $\beta$, an expression for the posterior producer's risk for the
exponential test plan $(T,c)$ is

@@

While our basic approach provides reasonable initial inferences, there are
several extensions to incorporate. For example, reliability estimates for
vehicles with no observed failures are sensible; however, we should leverage
more information across vehicles. Because the correlations induced by our
current model are fairly low, potential methods for inducing more correlation
between the vehicles in the related failure modes are being investigated. We
also need to look more closely at the intra-phase repair assumptions.  Appling
repairable system  methodology in the modeling and reliability assesment stage
could be a good approach, but this could  add a great deal of complexity to the
assurance planning stage.

>>>>

In this paper, we propose an alternative approach using a Bayesian hierarchical
model.  The methodology section is organized as follows.  In section 3.1 we
begin by introducing a general structure that models the relationships in the
data across all test phases while accounting for CAPs and incorporates known
similarities between vehicle failure modes.  Next, we will consider different
distributional assumptions and their implications.  Using the JLTV case study we
will illustrate the process of model selection using three different diagnostic
checks.  In section 3.2 we discuss methods of designing next stage test plans.
First we outline the traditional approaches, then we walk through a Bayesian
approach that allows the practitioner to incorporating the models developed from
section 3.1 with the hopes of reducing testing resources required while still
minimizing producer and consumer risks.

In this reliability setting we are analyzing time of failure data measured in
miles for a multiple component system with the primary objective being
assessment of the system failure rate and prediction of future failure counts.
The most common models used in this failure rate analysis are lifetime
distributions and the most common for failure count analysis is the
\emph{Poisson process} family of counting model.  We will utilize both and
specifically the relationships between them in planning future test.

\subsubsection{Model Structure}
Introducing notation, for each phase of testing we have failure mileage data for
a given vehicle $i$ and failure mode $j$ denoted as $t_{ij0}, t_{ij1},...,
t_{ijn_{ij}}, t_{ijc}$, where $t_{ij0} = 0$ and $t_{ijc}$ is the censored
observation at the end the testing phase. In each phase of testing, we assume
the vehicle miles between failures, $y_{ijk} = t_{ijk} - t_{ijk-1}$, follow a
lifetime distribution $f(\cdot)$, with an unknown set of parameters that include
a rate parameter.  For the first phase the rate parameter for vehicle $i$ and
failure mode $j$ will be denoted as $\lambda_{ij}$.  Then for the next stage we
will use the same $\lambda_{ij}$ but add a multiplicative correction parameter
$\rho_{j}^{P2}$ that represents the change in this rate due to the CAP.  This
procedure is then repeated for each subsequent stage.  The correction parameter
will be discussed more in the next section but the general model is as follows,
\begin{align*}
\text{Phase 1: }&y_{ijk}\mid\lambda_{ij}\sim f(\cdot), \quad i = 1,2,...,v \quad
j=1,2,...,s \quad k=1,2,...,n_{ij}\\
\text{Phase 2: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\sim f(\cdot) \\
\text{Phase 3: }&y_{ijk}\mid\lambda_{ij}\rho_{j}^{P2}\rho_{j}^{P3}\sim f(\cdot)
\end{align*}
where $v$ represents the number of vehicles, $s$ is the number of failure modes,
and $n_{ij}$ are the number of failures of vehicle $i$ failure mode $j$.

% The number of failure modes is assumed fixed and known \textit{a priori}.

For the model we assume a prior distribution on failure rate parameter
$\lambda_{ij}$.  This distribution depends on whether failure mode $j$ is
considered to be common across vehicles or related but not identical.  If
failure mode $j$ is considered common across vehicles we will assume there is a
single failure rate $\lambda_j$ that is shared by all eight vehicles with a
prior distribution that has positive support.  In the JLTV study we will use a
non-informative gamma distribution.  For failure modes that are considered
related across vehicles but not expected to be exactly the same, we place a
prior distribution on the collection of $\lambda_{ij}$; in other words, we
assume each of the vehicles has a distinct failure rate for failure mode $j$ but
they arise from a common distribution.  This is the common Bayesian hierarchical
modeling structure, where we then place  hyperprior distributions on the shared
distribution's parameters.  In the JLTV study we use a gamma distribution with
non-informative hyperpriors for all related failure modes.  Many times in
practice  it is difficult to know ahead of time if individual components should
be modeled  as common or related.  In the JLTV study we fit models for each
component with both model structures and used diagnostic tools  that are
discussed in a later section to make our final decision.

@@

One normal assumption used in reliability growth modeling is nondecreasing
failure rates; that is either the fixes were effective or had no effect, but did
not degrade the family of vehicles.  This should generally be the case, but
because we are dealing with complex systems and testing conditions are rarely
completely consistent, we will sometimes see decreases in failure rates after
adjustments are made.  Thus we will choose a prior distribution for the
correction parameter $\rho_{j}^{P2}$ that has positive support.  If
$\rho_{j}^{P2}$ is less than one, this represents an improvement in reliability.
And the same thinking is applied to $\rho_{j}^{P3}$ for the correction period
between phases two and three.  With this structure we can use the posterior
distributions of the correction parameters to make inference on the effectiveness
of the repairs and the join posterior distributions to evaluate the overall
system reliability within each phase.

@@

This is by far the most common parametric distribution used in reliability
modeling because of its desirable math mathematical properties and simple
interpretations.  One of the convenient properties, because we are assuming
independence between failure modes, is the overall system failures also follow
an exponential distribution with a system failure rate $\lambda_S =
\sum_{j}\lambda_{j}$.  A second, possibly less attractive property, is that the
hazard rate is constant over miles.  For the JLTV, setting this would assume that a given
component is equally likely to fail in the first mile of testing as it is in the
thousandth.  This may be reasonable for some reliability settings, but in most
setting we observe either a decreasing hazard rate where failures are likely to
occur early in testing but less likely as the test goes on, or increasing hazard
rate where we see the system wear down as the test progresses.

Despite its common uses the assumption of a constant hazard rate over time is
rarely justifiable.  It has been well documented the issues that can arise when
this assumption is violated ~\cite{ref3}.  Therefore we will also consider more
flexible distributions when analyzing the data.  In our analysis of the JLTV
data we fit the same hierarchical model structure using the Weibull as our
lifetime distribution $f(\cdot)$.  Now we assume that the failure mileage
$t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$ distribution with scale
parameter $\lambda$ and shape parameter $\gamma$, with probability density
function,
\begin{equation*}
    f(t_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
    t_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} t_{ijk}^{\gamma_{i}}).
\end{equation*}
The exponential is a special case of the Weibull, when $\gamma = 1$.  You should
notice here we are now modeling the actual failure mileage $t_{ijk}$ instead of
the miles between failures $y_{ijk}$.  This implies the "bad as old" assumption
for intra-test repairs.  We could have continued with the miles between failures
and assumed "good as new" repairs, but "bad as old" modeling will be more
convenient for developing assurance test plans in later sections.  This
distinction is important in the Weibull case because the failure rate is not
constant in time. In practice the decision on intra-test repair assumptions
should be made based on the application.  In many cases repairs should be
treated as somewhere between "good as new" and "bad as old".  This requires more
complex modeling that is beyond the scope of this paper.

@@

\subsubsection{JLTV Reliability}
We have discussed different models structures and distributional assumptions
that accompany them.  Using McMC we fit each of these models to the JLTV
dataset.\footnote{The likelihoods and sampling distributions are available in the
appendix.} Then we use the posterior distributions of the systems parameters to
estimate reliability-related quantities of interest for each of the eight
vehicle types.  We are able to look at a number of different statistics related
to reliability at both the component and system level.  In this study, one
quantity of interest is expected miles to failure(EMTF).  In figure 1 we have box
plots and summary statistics from the posterior distributions of the expected
miles to failure for one of the vehicle types for each of the three phases,
first using the exponential model and second using the more general Weibull
model.

@@

You can see the posterior EMTF distributions from the Weibull model have more
spread than the exponential.  This is generally expected, given the Weibull
model is estimating two model parameters to the exponentials one, but what is
concerning is that the center of the distributions is also quite different
between the two models.  The Weibull EMTF posterior means are consistently
larger than the exponentials.  We saw this across all eight vehicle types.  This
was the first indication that the exponential model may not be a good fit to the
data.

\subsubsection{Model Diagnostics}
As seen in the last section with the JLTV data, the decision of which model to
use can have a drastic impact on reliability assessment.  We will now look at a
few  goodness-of-fit methods that can be used to help in this decision.  The
first model selection question we will explore is the parametric form,
exponential versus Weibull.  This an example of the classic statistical modeling
the trade-off between fit and interpretability.  Because the Weibull is a more
flexible model it will always, in a sense, fit the data better, but this comes
at a price.  The exponentials convenient form makes both computation and
interpretation straightforward.  When the Weibull's shape parameter is
introduced this advantage is lost.  Thus, when the overall fit is close to the
same between the exponential and the Weibull we will default to using the
exponential.

The first check we used in decide between the exponential and Weibull models is
to fit the Weibull model and look at the posterior distributions of the shape
parameters and determine if one is a reasonable value.  Looking at the plot in
figure 2 from the Weibull model fit with the JLTV data, we see that one is
not a reasonable value for any of the failure modes.  This is another clue
that the exponential model is not be a good fit to this data.

\begin{figure}[h]
  \centering
      \includegraphics[width=8cm, height=7cm]{shapePostPlot}
  \caption{Posterior Plots of Weibull Shape Parameter}
\end{figure}

Now a more formal diagnostic tool, the Deviance information criterion (DIC)
~\cite{ref4}. This is a popular method for comparing the goodness of fit of
multiple models. The DIC method includes a penalty term that grows with the
numbers of unknown parameters in the model.  The DIC value is a unit-less
measure with lower values indicating a better fit to the data.  In the table
below we show the DIC results for the different distribution and structure
combinations, we considered with the JLTV dataset.

% need to recheck these numbers %
\begin{table}[h]
\centering
\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Common Rate Model                     & 21,264.19             \\
              & Hierarchical Rate Model               & 21,244.47             \\
Weibull       & Common Rate Model                     & 20,658.25             \\
              & Hierarchical Rate Model               & \textbf{17,908.06}    \\
\hline
\end{tabular}
\caption{JLTV DIC Results}
\label{table:ta}
\end{table}

The results in table 1 shown that the hierarchical Weibull model fits the data
much better than the exponential, but in general information criteria
comparisons do not tell us if the model is truly a good representation of the
underlying process. The last model diagnostics method we present is called
posterior predictive checking ~\cite{ref5}.  Here we start with important
features of the data that we would expect to see if the experiment was repeated,
these are usually provided by practitioner with knowledge about the random
process being studied. In the JLTV case one feature we were interested in was
the number of miles between failure observations that were less than 140 miles.
We then used the final models to simulate 5,000 new datasets for vehicles tested
over the same number of miles for each of the three phases. We then plot the
resulting distributions for each of the 8 vehicles for all 3 phases.  In Figure
3 are two examples of the boxplots produced, one from the exponential model
(left) and one from the Weibull model (right), with the dashed line showing
where the value from the observed dataset fell.  For this method we don’t expect
all of the true values to fall in the center of the distribution. Some values in
the tales are to be expected in a random processes like this one, but when we
see many observations in the tails, as we do with the exponential, we should
consider other modeling options.

@@

\subsection{Assurance Test Planning}
In this section, we will use the reliability models fit in section two to
develop a plan for future testing.  Here the objective is to demonstrate, at
a desired level of confidence, that the system will meet or exceed a specified
requirement. The methods to be employed will be similar to the assurance testing
as discussed by Hamada et al. ~\cite{ref6}. Bayesian \emph{reliability assurance
tests} are used to ensure that the reliability of an item meets or exceeds a
specified requirement with a desired probability. Meeker and Escobar
~\cite{ref7} established the difference between this and the more traditional
\emph{reliability demonstration test}.  The difference being that the assurance
test plan incorporates supplementary data and information, where the
demonstration test only uses test data.

In most test planning settings we are interested in controlling error rates
while minimizing the resources required for testing.  In the DoD acquisition
process, the error rates are referenced in terms of risk. \emph{Consumer
risk} which considers the event of purchasing a product that does not meet
reliability requirements.  \emph{Producer risk} which considers the event of a
product with acceptable reliability failing a given test and not being
considered for purchase.  Introducing the notation for this section, in the JLTV
case study, we will be determining how many miles on test $T$, are required and
how many system failures to allow $c$, before the product is considered
unacceptable.  We will define $W(t)$ as a random variable that represents the
total number of system failures after $t$ miles.  We will let $\pi$ denote the
quantity of interest that is related to system reliability at a given time. It
is common to base both classical and Bayesian test plans on two specified levels
of $\pi$: $\pi_0$, an \emph{acceptable reliability level} (ARL), and $\pi_1$, a
\emph{rejectable reliability level} (RRL), where $\pi_1 \leq  \pi_0$. Although
the precise definition of ARL and RRL differ between the classical and Bayesian
test criteria, we use them in an equivalent way.

\subsubsection{Classical Approach}
In the frequentest (classical) test planning setting the risk criteria
are as follows. The \emph{producer's risk}, defined as the probability of
failing the test under the null hypothesis $\pi = \pi_0$, and the
\emph{consumer's risk}, defined as the probability of passing the test under an
alternative hypothesis $\pi = \pi_1$.  Suppose that we specify a maximum value,
$\alpha$, of the producer's risk and a maximum value, $\beta$, of the consumer's
risk. For test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failures $W(t)$ and the reliability $\pi$.  Then we can simply find
the combinations of these probabilities by simultaneously solving these two
equations.  In the case where the component failure times are assumed to be
exponentially distributed with rate parameter $\lambda_i$ the failure counts for
each component come from a homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
this classical test planning approach.

\subsubsection{Bayesian Approach}
The classical methods for determining the testing procedure rely only on
distributional assumptions or asymptotic results. With a Bayesian approach we
incorporate the supplementary data from the previous testing phases with the
hopes of minimizing the resources needed for testing.

@@

For a test that fails, the \emph{posterior producer's risk} is the probability
that $\pi \geq \pi_{0}$, or $P \text{(}\pi \ge \pi_0 \vert \text{Test Is
Failed)}$. Notice that this is simply the posterior probability that $\pi \ge
\pi_0$ given that we have observed more than $c$ failures. In the exponential
case, if we let $\pi$ be the system failure rate $\lambda_S$ and $\pi_0$ be
predetermined acceptable failure rate $\lambda_0$, then using Bayes' Theorem,
and assuming a maximum allowable posterior producer's risk $\alpha$, an
expression for the posterior producer's risk for the exponential test plan
$(T,c)$ is
$$
\begin{aligned}
    P(\lambda_S \geq \lambda_0 \; \vert \; \text{Test Is Failed)} &= P(\lambda_S
    \geq \lambda_0 \; \vert \; W > c) \\ &= \int_{\lambda_0}^{\infty}
    p(\lambda_S \; \vert W > c) d\lambda_S \\ &= \int_{\lambda_0}^{\infty}
    \frac{f(W > c \vert \lambda_S)}{\int_{0}^{\infty} f(W > c \vert \lambda_S)
    d\lambda_S} d\lambda_S \\ &= \frac{\int_{\lambda_0}^{\infty} 1 - [ \sum_{W=0}^c
    \frac{(\lambda_S T)^W exp(-\lambda_S T)}{W!}]p(\lambda_S)d\lambda_S}
    {\int_{0}^{\infty} 1 - [ \sum_{W=0}^c \frac{(\lambda_S T)^W exp(-\lambda_S
    T)}{W!}]p(\lambda_S)d\lambda_S} \leq \alpha
\end{aligned}
$$
\\
\\
For simplicity we if fix c to be zero and then perform Monte Carlo integration
using N posterior draws $ \lambda_S^{(j)} $
$$
\begin{aligned}
	 P(\lambda_S \geq \lambda_0 \; \vert \; W = 0) &=
	 \frac{\int_{\lambda_0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S}
	 {\int_{0}^{\infty} 1 - exp(-\lambda_S T)p(\lambda_S)d\lambda_S} \\ &\approx
	 \frac{\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)I(\lambda_S^{(j)} \geq
	 \lambda_0)} {\sum_{j = 1}^{N} 1 - exp(-\lambda_S^{(j)} T)} \end{aligned}
$$

Similarly, given that the test is passed, the \emph{posterior consumer's risk}
is the probability that $\pi \leq \pi_1$, or $P \text{(}\pi \leq \pi_0 \vert
\text{Test Is Passed)}$.  Now we let $\pi_1$ be a predetermined rejectable
failure rate $\lambda_1$ and assuming a maximum allowable posterior consumer's
risk $\beta$, an expression for the posterior producer's risk for the
exponential test plan $(T,c)$ is

@@

While our basic approach provides reasonable initial inferences, there are
several extensions to incorporate. For example, reliability estimates for
vehicles with no observed failures are sensible; however, we should leverage
more information across vehicles. Because the correlations induced by our
current model are fairly low, potential methods for inducing more correlation
between the vehicles in the related failure modes are being investigated. We
also need to look more closely at the intra-phase repair assumptions.  Applying
repairable system methodology in the modeling and reliability assessment stage
could be a good approach, but this could  add a great deal of complexity to the
assurance planning stage.
